---
title: "Appendices"
author: "Zack Eisman"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    toc_collapsed: true
    theme: lumen
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE)
```


```{r include = FALSE}
# Load any packages you may need here

library(car)
library(ggplot2)
library(gridExtra)
```


```{r include = FALSE}
# Read in your data set here (and perform any necessary cleaning/manipulation)

fifa <- read.csv("fifa.csv")
fifa <- subset(fifa, league_name == 'English Premier League' | league_name == 'Spain Primera Division' | league_name == 'Italian Serie A' | league_name == 'German 1. Bundesliga' | league_name == 'French Ligue 1')
```

***

### Figure 1: Initial Model

```{r}
lm_initial <- lm(potential ~ overall + age + value_eur + league_name, data = fifa)
summary(lm_initial)
```

```{r}
plot(lm_initial, which = 1, id.n = 0, add.smooth = FALSE)
```

```{r}
plot(lm_initial, which = 2, id.n = 0)
```

***

### Figure 2: Histograms of All Variables

```{r}
p1 <- ggplot(data = fifa, aes(x = potential)) + 
  geom_histogram(bins = 8, color = "black", fill = "grey80") + 
  labs(title = "Histogram of Potentials",
       x = "Potential Overall",
       y = "Frequency") + 
  theme_bw()

p2 <- ggplot(data = fifa, aes(x = overall)) + 
  geom_histogram(bins = 8, color = "black", fill = "grey80") + 
  labs(title = "Histogram of Overalls",
       x = "Player Overalls",
       y = "Frequency") + 
  theme_bw()

p3 <- ggplot(data = fifa, aes(x = age)) + 
  geom_histogram(bins = 8, color = "black", fill = "grey80") + 
  labs(title = "Histogram of Ages",
       x = "Age (in years)",
       y = "Frequency") + 
  theme_bw()

p4 <- ggplot(data = fifa, aes(x = log(age))) + 
  geom_histogram(bins = 8, color = "black", fill = "grey80") + 
  labs(title = "Histogram of log(Ages)",
       x = "log(Ages)",
       y = "Frequency") + 
  theme_bw()

p5 <- ggplot(data = fifa, aes(x = value_eur)) + 
  geom_histogram(bins = 8, color = "black", fill = "grey80") + 
  labs(title = "Histogram of Transfer Values",
       x = "Transfer Value (in euros)",
       y = "Frequency") + 
  theme_bw()

p6 <- ggplot(data = fifa, aes(x = log(value_eur))) + 
  geom_histogram(bins = 8, color = "black", fill = "grey80") + 
  labs(title = "Histogram of log(Transfer Value)",
       x = "log(Transfer Value)",
       y = "Frequency") + 
  theme_bw()

grid.arrange(p1, p2, p3, p4, p5, p6, nrow = 3, ncol = 2)
```

***

### Figure 3: Improved Residuals vs Fitted Graph

```{r}
lm_logs <- lm(potential ~ overall + log(age) + log(value_eur) + league_name, data = fifa)
plot(lm_logs, which = 1, id.n = 0, add.smooth = FALSE)
```

***

### Figure 4: Scatterplot Matrix of Data

```{r}
plot(~ potential + overall + log(age) + log(value_eur), data = fifa)
```

***

### Figure 5: Improved Model

```{r}
lm_improved <- lm(potential ~ overall + log(age) + log(value_eur) + league_name, data = fifa)
summary(lm_improved)
```

***

### Figure 6: Interaction Plot

```{r}
ggplot(data = fifa, aes(x = overall, y = potential, col = league_name, shape = league_name)) + 
  
  geom_point() +
  
  geom_smooth(method = "lm", formula = y ~ x, se = FALSE) +
  
  labs(title = "Player Potential vs Overall by League",
       x = "Player Overall",
       y = "Potential Overall") +
  
  theme_bw()
```

***

### Figure 7: Interaction Model

```{r}
lm_interaction <- lm(potential ~ overall + log(age) + log(value_eur) + league_name + league_name * overall, data = fifa)
summary(lm_interaction)
```

***

### Figure 8: Removing Transfer Value Model

```{r}
lm_swap <- lm(potential ~ overall + log(age) + log(wage_eur) + league_name + league_name * overall, data = fifa)
summary(lm_swap)
```

```{r}
p7 <- ggplot(data = fifa, aes(x = wage_eur)) + 
  geom_histogram(bins = 8, color = "black", fill = "grey80") + 
  labs(title = "Histogram of Player Wages",
       x = "Wage (in euros)",
       y = "Frequency") + 
  theme_bw()

p8 <- ggplot(data = fifa, aes(x = log(wage_eur))) + 
  geom_histogram(bins = 8, color = "black", fill = "grey80") + 
  labs(title = "Histogram of log(Wage)",
       x = "log(Wage)",
       y = "Frequency") + 
  theme_bw()

grid.arrange(p7, p8, nrow = 1, ncol = 2)
```

```{r}
plot(lm_swap, which = 1, id.n = 0, add.smooth = FALSE)
```

***

### Figure 9: Final Model

```{r}
lm_final <- lm(potential ~ overall + log(age) + log(wage_eur) + league_name + league_name * overall, data = fifa)
summary(lm_final)
```

```{r}
plot(lm_final, which = 1, id.n = 0, add.smooth = FALSE)
```

```{r}
plot(lm_final, which = 2, id.n = 0)
```

```{r}
vif(lm(potential ~ overall + log(age) + log(wage_eur), data = fifa))
```


***

### Figure 10: CMF (Final Model)

$E(Y_{potential}|X) = \beta_0 + \beta_1 X_{overall} + \beta_2 log(X_{age}) + \beta_3 log(X_{wage}) +  \beta_4 I_{Ligue 1} + \beta_5 I_{Bundesliga}  + \beta_6 I_{SerieA}  + \beta_7 I_{La Liga} + \beta_8 X_{overall}I_{Ligue 1} + \beta_9 X_{overall}I_{Bundesliga} + \beta_{10}  X_{overall}I_{SerieA} + \beta_{11} X_{overall}I_{LaLiga}$



```{r include = FALSE}
# IMPORTANT NOTES

# The plots above are examples! 
# You will have more plots and output than what is shown above
# Please see the submission guidelines file for more information

# Be sure your "setup" code chunk at the top is set to `echo = FALSE`
# Including *** between figures adds in some space to your knitted file
# Be sure to leave a blank line of code before and after the line with ***
```







